Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-02-22 Paper/Manuscript.tex
Changed from Psi to Psi_e in MS
Added functions to calculate power(f)

Echoes from multiple scatterers can be quantified using volume backscattering strength, $\sv$, being the density of backscattering cross sections, and is given by:
%
\begin{equation}
\label{eq:sv}
\sv  =  10\log_{10}\frac{\sum\bs}{V}.
\end{equation}
%
where $V$ is the volume occupied by the scattering targets. The power-budget equation for multiple targets is then:
%
\begin{equation}
\label{eq:sv_f}
\sv(\freqsym) = 10\log_{10}(\prxevf(\freqsym)) + 20\log_{10}(\range_c) + 2\absorp(\freqsym)\range_c 
- 10\log_{10}\left( \frac{\ptxe \wlen^2 \cw \tslide \eqang(\freqsym) \gainzero^2(\freqsym)}{32\pi^2} \right), 
\end{equation}
%
where $\prxevf(\freqsym)$ is the received electric power in a matched load for the signal from a volume at frequency $\freqsym$, $\cw$ the sound speed, $\tslide$ the duration of the time window, excluding the zero-padded portion if applied, used for evaluating the frequency spectrum, $\range_c$ is the range to the centre of the range volume covered by $\tslide$, and $\eqang$ is the two-way equivalent beam angle. The two-way equivalent beam angle is a function of frequency that is derived from an empirical estimate of $\eqang$ at the nominal frequency, $\fn$:
\begin{equation}
\label{eq:PsiFc}
\eqang(f) = \eqang(\fn)\left(\frac{\fn}{f}\right)^2.
\end{equation}

@@

The normalised Hanning window, $\hannwnorm$, is given by: 
%
\begin{equation}
\label{eq:hannw}
\hannwnorm(\genidxsym) = \frac{\hannw(\genidxsym)}{\left( \frac{||\hannw||_2}{\sqrt{\nw}} \right)}, i = \frac{-\nw}{2}, \ldots, \frac{\nw}{2}
\end{equation}
%
and the discrete Fourier transform of the windowed data, $\ypcvolumef(\samplesymf)$, is then obtained from:
%
\begin{equation}
\label{eq:FFT_volume}
\ypcvolumef(\samplesymf) = \dft_\ndft 
\left( \hannwnorm(\genidxsym) \left(\ypcspread (\genidxsym+\samplesymt) \left[ u(\genidxsym + \frac{\nw}{2}) - u(\genidxsym - \frac{\nw}{2}) \right] \right) \right),
\end{equation}
%
where $u(\genidxsym)$ is the step function and $\samplesymt$ is the sample data index for the centre of the sliding window. The discrete Fourier transform of the auto correlation function of the matched filter signal, $\ymfautof(\samplesymf)$, also needs to be evaluated at the same frequencies:
%
\begin{equation}
\label{eq:FFT_TX_Auto}
\ymfautof(\samplesymf)  =  \dft_\ndft (\ymfauto(\samplesymt)).
\end{equation}
%
The normalized discrete Fourier transform of the windowed data, $\ypcvolumenormf(\samplesymf)$, is then given by:
%
\begin{equation}
\label{eq:FFT_volume_norm}
\ypcvolumenormf(\samplesymf) = \frac{\ypcvolumef(\samplesymf)}{\ymfautof(\samplesymf)},
\end{equation}
%
and received power into a matched load, $\prxevf(\samplesymf)$, is estimated from:
%
\begin{equation}
\label{eq:prx_FFT_volume}
\prxevf(\samplesymf) = \nchannels \left( \frac{|\ypcvolumenormf(\samplesymf)|}{2\sqrt{2}} \right)^2 \left( \frac{|\zrxe+\ztde|}{|\zrxe|}\right)^2 \\
\frac{1}{|\ztde|}. % All channels (*4), matched load (/2), and effective values (/sqrt(2))
\end{equation}
%
Finally, the discretized estimate of $\sv(\freqsym)$, $\sv(\samplesymf)$, is given by:
%
\begin{equation}
\label{eq:Sv_FFT}
\sv(\samplesymf) = 10\log_{10}(\prxevf(\samplesymf)) + 2\absorp(\samplesymf) \range_c \\
- 10\log_{10}\left( \frac{\ptxe \wlen^2 \cw \tslide \eqang(\samplesymf) \gainzero^2(\samplesymf) }{32\pi^2} \right).
\end{equation}

>>>>

Echoes from multiple scatterers can be quantified using volume backscattering strength, $\sv$, being the density of backscattering cross sections, and is given by:
%
\begin{equation}
\label{eq:sv}
\sv  =  10\log_{10}\frac{\sum\bs}{V}.
\end{equation}
%
where $V$ is the volume occupied by the scattering targets. The power-budget equation for multiple targets is then:
%
\begin{equation}
\label{eq:sv_f}
\sv(\freqsym) = 10\log_{10}(\prxevf(\freqsym)) + 20\log_{10}(\range_c) + 2\absorp(\freqsym)\range_c 
- 10\log_{10}\left( \frac{\ptxe \wlen^2 \cw \tslide \eqang(\freqsym) \gainzero^2(\freqsym)}{32\pi^2} \right), 
\end{equation}
%
where $\prxevf(\freqsym)$ is the received electric power in a matched load for the signal from a volume at frequency $\freqsym$, $\cw$ the sound speed, $\tslide$ the duration of the time window, excluding the zero-padded portion if applied, used for evaluating the frequency spectrum, $\range_c$ is the range to the centre of the range volume covered by $\tslide$, and $\eqang$ is the two-way equivalent beam angle. The two-way equivalent beam angle is a function of frequency that is derived from an empirical estimate of $\eqang_e$ at the nominal frequency, $\fn$:
\begin{equation}
\label{eq:PsiFc}
\eqang(f) = \eqang_e(\fn)\left(\frac{\fn}{f}\right)^2.
\end{equation}

@@

TODO: Explain edge cases.

The normalised Hanning window, $\hannwnorm$, is given by: 
%
\begin{equation}
\label{eq:hannw}
\hannwnorm(\genidxsym) = \frac{\hannw(\genidxsym)}{\left( \frac{||\hannw||_2}{\sqrt{\nw}} \right)}, i = \frac{-\nw}{2}, \ldots, \frac{\nw}{2}
\end{equation}
%
and the discrete Fourier transform of the windowed data, $\ypcvolumef(\samplesymf)$, is then obtained from:
%
\begin{equation}
\label{eq:FFT_volume}
\ypcvolumef(\samplesymf) = \dft_\ndft 
\left( \hannwnorm(\genidxsym) \left(\ypcspread (\genidxsym+\samplesymt) \left[ u(\genidxsym + \frac{\nw}{2}) - u(\genidxsym - \frac{\nw}{2}) \right] \right) \right),
\end{equation}
%
where $u(\genidxsym)$ is the step function and $\samplesymt$ is the sample data index for the centre of the sliding window. The discrete Fourier transform of the auto correlation function of the matched filter signal, $\ymfautof(\samplesymf)$, also needs to be evaluated at the same frequencies:
%
\begin{equation}
\label{eq:FFT_TX_Auto}
\ymfautof(\samplesymf)  =  \dft_\ndft (\ymfauto(\samplesymt)).
\end{equation}
%
TODO: How to index samples along range? In the code \_n is used to indicate the range component of the FFt's. Needs attention.

The normalized discrete Fourier transform of the windowed data, $\ypcvolumenormf(\samplesymf)$, is then given by:
%
\begin{equation}
\label{eq:FFT_volume_norm}
\ypcvolumenormf(\samplesymf) = \frac{\ypcvolumef(\samplesymf)}{\ymfautof(\samplesymf)},
\end{equation}
%
and received power into a matched load, $\prxevf(\samplesymf)$, is estimated from:
%
\begin{equation}
\label{eq:prx_FFT_volume}
\prxevf(\samplesymf) = \nchannels \left( \frac{|\ypcvolumenormf(\samplesymf)|}{2\sqrt{2}} \right)^2 \left( \frac{|\zrxe+\ztde|}{|\zrxe|}\right)^2 \\
\frac{1}{|\ztde|}. % All channels (*4), matched load (/2), and effective values (/sqrt(2))
\end{equation}
%
Finally, the discretized estimate of $\sv(\freqsym)$, $\sv(\samplesymf)$, is given by:
%
\begin{equation}
\label{eq:Sv_FFT}
\sv(\samplesymf) = 10\log_{10}(\prxevf(\samplesymf)) + 2\absorp(\samplesymf) \range_c \\
- 10\log_{10}\left( \frac{\ptxe \wlen^2 \cw \tslide \eqang(\samplesymf) \gainzero^2(\samplesymf) }{32\pi^2} \right).
\end{equation}
